A fast and Low-Overhead Technique to Secure Programs Against Integer Overflows

### 2012-09-05 doc/Manuscript/CGO/paper.tex

\usepackage{amsmath}
\usepackage{graphicx}
\usepackage{mathpartir} % To use \inferrule
\usepackage{amssymb}    % To use \mathbb
\usepackage{skak}

@@

>>>>

\usepackage{amsmath}
\usepackage{graphicx}
\usepackage{mathpartir} % To use \inferrule
\usepackage{amssymb}    % To use \mathbb
\usepackage{skak}
\usepackage{pbox}

@@

%How we have done the dynamic tests  
We have executed the instrumented programs of the integer benchmarks of SPEC
2006 CPU to measure the overhead produced by our instrumentation in 
real world programs.
To do this, we have developed a little test framework that compiles, runs and
collects the statistics about the execution of all the programs of SPEC 2006.
The execution of the programs was made using the arguments and inputs of the "test"
mode, which is faster to execute than the "ref" inputs.

%Analysis about the Table 1 of the spreadsheet (Unpruned Instrumentation)
Figure~\ref{fig:unpruned_analysis} shows the number of instructions that has
received instrumentation, without avoiding inserting the instrumentation by
using any static analysis. We can see that the number of these instructions is low 
(3,96 in the average). 
Figure~\ref{fig:prunning_analysis} shows that it is possible to use static 
analysis to avoid inserting the instrumentation in some instructions.
